---
title: "The Documentatiokn for comm Utilities"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

## The echo_msg 

The echo_msg function is a utility function that prints a formatted message to the console and, optionally, to a log file. It takes the following parameters:

prg: A string representing the program or module generating the message.
step: A float or integer indicating the current step or progress in the program.
msg: The message to be printed.
lvl: An optional integer for the message level (default is 0). Messages with a level less than or equal to the global or debug level will be printed.
fn: An optional string representing the log file's name. If not provided, it will use the log file name specified in the environment variable log_fn.
The function first retrieves several environment variables, such as g_lvl, d_lvl, log_fn, write2log, QUERY_STRING, and HTTP_HOST. These variables are used to configure the function's behavior based on the environment.

The function then processes the msg parameter to hide any passwords that might be included in the message using regular expressions. If the function is being executed in a web environment, it prints the message with appropriate HTML formatting.

Finally, if the message level lvl is less than or equal to the global or debug level, the message is printed to the console. If the ofn (output file name) and wrt2log (write to log) variables are set, the message is also written to a log file.

The echo_msg function can be used for logging and debugging purposes, offering both console and file output with different formatting for web and non-web environments.

